INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-11-10 paper.tex
Poznamky k abstraktu

\begin{abstract}
JetBrains MPS is a language workbench, an IDE that allows developers both to write code and manipulate language definitions.
It leverages the concept of projectional editing, where the developer directly manipulates the AST representation of program code.
While MPS focuses on domain-specific languages (DSL), it needs to support also general-purpose programming languages (GPLs) --- for example, to compile and run programs written in some DSL, or to enable combination of GPLs with languages created in MPS.

>>>>

\begin{abstract}
\PV{Manipulate language definitions mozna uplne neevokuje tvorbu jazyku. Slo by to rict vic polopaticky? Tady mozna pomuze vic Vaclav.}
JetBrains MPS is a language workbench, an IDE that allows developers both to write code and manipulate language definitions.
It leverages the concept of projectional editing, where the developer directly manipulates the AST representation of program code.
While MPS focuses on domain-specific languages (DSL), it needs to support also general-purpose programming languages (GPLs) --- for example, to compile and run programs written in some DSL, or to enable combination of GPLs with languages created in MPS.
